Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-03-17 paper/manuscript.Rmd
minor eds

<!-- add numbers in here -->
In total, these 86 swimming events occurred in month (n = Y), month (n = Y), and
month (n = Y), while the remaining events were in month, month, and month (n =
Y). On average, caribou swam between islands approximately ever 24 days, but
some individuals swam up to XX times per week/month/whatever. <!--Is it better
to just state our results here, or give this sort of teaser? Initially I had "86
events by 3 individuals" here, but then we ignore that for a couple paragraphs
of context before getting back into it... which seemed weird-->

@@

Caribou may swim between islands in the ocean for similar reasons that drive
caribou swimming in freshwater [@Leblond2016]. We propose that one such
explanation, the forage limitation hypothesis, is likely driving these oceanic
swimming events [@Miller2002].

@@

**Forage limitation**

>>>>

<!-- add numbers in here -->
In total, these XX swimming events occurred throughout the ice-free season, with a peak in November. On average, caribou swam between islands approximately ever XX days, but
some individuals swam up to XX times per week/month/whatever. <!--Is it better
to just state our results here, or give this sort of teaser? Initially I had "86
events by 3 individuals" here, but then we ignore that for a couple paragraphs
of context before getting back into it... which seemed weird-->

@@

Caribou may swim between islands in the ocean for similar reasons that drive
caribou swimming in freshwater [@Leblond2016]. We propose that one such
explanation, the forage limitation hypothesis, is likely driving oceanic
swimming events [@Miller2002].

@@
